Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Finalised RQ1.

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
\caption{FIXME Maybe merge with Table 7? <-- You mean Table 9?}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
\hline
\textit{good} & 2,308 & 92 & 66 & \\
\textit{ok'} & 11,749 & 136 & 39 & \\
$S_D'$ & 17,081 & 471 & 76 & \\
$N_D'$ & 88 & 77 & 29 & \\
\hline
Total & 31,946 & 621 & 95 &
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in FIXME, for the 2,308 \textit{good} pairs,
there are 92 Stack Overflow snippets which are associated with 66
Qualitas projects. The 11,749 \textit{ok'} pairs are clones between
136 Stack Overflow snippets and 39 Qualitas projects.  Moreover, for
the disagreed pairs, we found 17,081 clone pairs reported by $S_D'$
are clones between 471 Stack Overflow snippets and 76 Qualitas
projects and 88 $N_D'$ clone pairs are clones between 77 Stack
Overflow snippets and 29 Qualitas projects. In total we found that the
manually investigated 31,946 clones pairs are clones between 621
Stack Overflow snippets and 95 Qualitas projects.

\textbf{To answer RQ1, with the four configurations of Simian and
  NiCad, we found most Qualitas projects to share similar code with
  Stack Overflow code snippets. When onlly considering the manually
  investigated snippets, FIXME}

\FIXME{Should we have removed the AC clones right at the beginning?}

@@

\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (28,642) or accidental clones (2,529) \FIXME{IN+AC here?} with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  178 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

@@

\section{Conclusions}
Online code clones are clones that have been copied to Q\&A websites such as Stack Overflow. They are similar to clones in software projects where they can be outdated and violating software license but are much harder to detect. We studied the online code clones between Stack Overflow and Qualitas projects, especially 3,632 clone pairs, manually in details.

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}

>>>>

The statistics on clones obtained from running Simian and NiCad are
presented in \Cref{tab:raw_stats}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with all 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
\caption{Investigated online clone pairs and snippets \FIXME{maybe
    merge with tables 7 and/or 9}}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
\hline
\textit{good} & 2,308 & 92 & 66 & \\
\textit{ok'} & 11,749 & 136 & 39 & \\
$S_D'$ & 17,081 & 471 & 76 & \\
$N_D'$ & 88 & 77 & 29 & \\
\hline
Total & 31,946 & 621 & 95 &
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,308
\textit{good} pairs, there are 92 Stack Overflow snippets which are
associated with 66 Qualitas projects. The 11,749 \textit{ok'} pairs
are clones between 136 Stack Overflow snippets and 39 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 471 Stack Overflow
snippets and 76 Qualitas projects and 88 $N_D'$ clone pairs are clones
between 77 Stack Overflow snippets and 29 Qualitas projects. In total
we found that the manually investigated 31,946 clones pairs are clones
between 621 Stack Overflow snippets and 95 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. Depending on the
  data set, between 82 to all 111 projects share similar code. This
  holds even for the investigated data set where 95 projects share
  code with Stack Overflow.}

%\FIXME{Should we have removed the AC clones right at the beginning?}

@@

%FIXME: We probably have to discuss IN clones.
%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (28,749) or accidental clones (2,418) with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  197 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

@@

\FIXME{This needs rewriting}

@@

\section{Conclusions}

\FIXME{This needs rewriting}

Online code clones are clones that have been copied to Q\&A websites
such as Stack Overflow. They are similar to clones in software
projects where they can be outdated and violating software license but
are much harder to detect. We studied the online code clones between
Stack Overflow and Qualitas projects, especially 3,632 clone pairs,
manually in details.

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc}
